---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# quasardb

The quasardb package is the official R API for [quasardb](https://www.quasardb.net) timeseries database.

## Installation

<!-- TODO:
You can install the released version from CRAN with:
```{r installation, eval = FALSE}
install.packages("quasardb")
```
-->

You can install quasardb from [GitHub](https://github.com/bureau14/qdb-api-r) with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("bureau14/qdb-api-r")
```

```{r include = FALSE}
# default values
knitr::opts_chunk$set(message = TRUE, warning = TRUE)
```

### quasardb C API

To build the R API, you will need the C API. It can either be installed on the machine (e.g. on UNIX in `/usr/lib` or `/usr/local/lib`) or you can unpack the C API archive in `qdb` directory. You can get the C API as well as other tools from [our download page](https://www.quasardb.net/-Get-).

### Building the extension from source

*NOTE: Commands to be executed from when source directory is the current working directory.*

To perform a clean build:
```{bash eval = FALSE}
R INSTALL --preclean --no-multiarch --with-keep.source .
```

To check the extension:
```{r eval = FALSE}
devtools::check()
```

To test the extension:
```{r eval = FALSE}
devtools::test()
```

## Usage

```{r message = FALSE, warning = FALSE}
library(quasardb)
```

Get underlying C API version:

```{r example}
qdb_version()
```

## TODO

 - Make a quasardb driver compliant with [DBI package](https://www.rdocumentation.org/packages/DBI/)
